Methodology for Assessing the State of the Practice for Domain X

### 2020-10-25 StateOfPractice/Methodology/Methodology.tex
added comments on "Measure Using Measurement Template"

\pmi{first pass for `tricky parts'; under summary information:
	``Publications about the software''
	list of publications can be found on some software websites, for others you may use google scholar or similar indexes,
	``Is there evidence that performance was considered?''	Look for mention of any items, broad scope to answer yes but must include explanatory text: speed, storage, throughput consideration as well as comments on performance optimization/development, GPU processing, parallelism, multicore processing, or similar considerations}

>>>>

\pmi{first pass for `tricky parts'; under summary information:
	``Publications about the software''
	list of publications can be found on some software websites, for others you may use google scholar or similar indexes,
``Is there evidence that performance was considered?'' Look for mention of any
items, broad scope to answer yes but must include explanatory text: speed,
storage, throughput consideration as well as comments on performance
optimization/development, GPU processing, parallelism, multicore processing, or
similar considerations} \ad{For ``performance'', the powerful search function
from Github can help. What I did is searching ``performance'' in the repo on
github.com, and usually I can get some author's comments regarding it. For
projects not hosting on github (e.g. on SourceForge), I just upload it as my own
repo, then to the search.}

\ad{Tricky parts: (1). I second ``Publications'' - it's really hard to search by
the software name sometimes. For example, I have software with names such as
``DICOM Viewer'' and ``GATE''. (2). ``Initial release date'' - it's very hard to
find the exact date, so for most of them, I used the release year. (3).
``continuous integration'' - sometimes it's hard to find out from the repo if
the authors don't mention it in any document. (4). ``getting started tutorial''
vs ``user manual'' - many projects don't have a clear distinction between these
two.}

\ad{Tricky parts: (1). I second ``Publications'' - it's really hard to search by
the software name sometimes. For example, I have software with names such as
``DICOM Viewer'' and ``GATE''. (2). ``Initial release date'' - it's very hard to
find the exact date, so for most of them, I used the release year. (3).
``continuous integration'' - sometimes it's hard to find out from the repo if
the authors don't mention it in any document. (4). ``getting started tutorial''
vs ``user manual'' - many projects don't have a clear distinction between these
two.}

\ad{Might need improvements: ``Are constants (other than 0 and 1) hard coded
into the program? (\{yes, no* , unclear\})''. Why we need extra comments if the
answer is ``no''?}
